---
title: "Pin_pit status"
output: html_document
---

# DO NOT RERUN MANUALLY UNLESS YOU HAVE A BACKUP 

## Instructions:

- Make sure you have kingpin installed
- Make sure you have CONNECT_SERVER and CONNECT_API_KEY_PHINTEL environmental variables in your .Renviron file
- Deploy this .Rmd to your RSConnect board and schedule to run every day at the time of your choosing. 
- Do not manually rerun after all this is set up. Let the automated schedule run this script and nothing more. 

```{r update, echo=FALSE, message=FALSE, warning=FALSE}
devtools::install_github("herts-phei/kingpin")
library(kingpin)

board <- board_rsconnect(Sys.getenv("CONNECT_SERVER"), 
                         Sys.getenv("CONNECT_API_KEY_PHINTEL"))
pin_pit <- kingpin::pin_return(board, "pin_pit")

# DELETE PIN IF DEADLINE REACHED
pin_pit <- lapply(pin_pit, function(x) {
  if (grepl("0", x$countdown)) {
    x <- NULL # remove
  } else {
    x$countdown <- paste0(as.numeric(substr(x$countdown, 1, 1)) - 1, " days to deletion") # count down 
    return(x)
  }
}) |>
  purrr::discard(is.null)

# REPIN
kingpin::pin_throw(board, pin_pit, "pin_pit")

```

## Pins to be deactivated 

```{r table, echo=FALSE}
data.frame(Pin = names(pin_pit),
           Countdown = sapply(pin_pit, function(x) x$countdown)) |>
  reactable::reactable(rownames = F)
```
